---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hlsmanager

<!-- badges: start -->
<!-- badges: end -->
## Key features

The goal of hlsmanager is to simplify to work with the HLS dataset from NASA. When downloaded from NASA AppEEARS; all the bands get saved as on tiff-file and the user has to merge them based on their filename. With this package is easy to get:
  1. an overview about the data you downloaded  
  2. merge them based on the default filename
  3. cloud mask them 
  
The data can be downloaded from: https://appeears.earthdatacloud.nasa.gov/?_ga=2.43130661.1417310973.1723470150-437277444.1719598629
All the steps are consecutive and can be considered the first part of your workflow. 
## Example

This is a basic example which shows you how to solve a common problem:

```{r}


summary_df <- hlsmanager::auto_df("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/tiffsasdownloaded") # HLS data as downloaded
head(summary_df)

```


```{2. Grouping the bands to individual scenes}

autogroup("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/tiffsasdownloaded", "C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/grouped")

print(paste("Number of files downloaded",length(list.files("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/tiffsasdownloaded"))))

print(paste("Number of files grouped",length(list.files("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/grouped"))))

terra::plot(terra::rast(list.files("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/grouped", full.names=T)[1])[[1:2]])
```

```{3. Applying the cloud mask to the grouped files}

#auto_mask("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/grouped", "C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/masked",   filterClouds = TRUE, filterAdjacent = TRUE, filterCloudshadow = TRUE, filterSnowice = FALSE, filterWater = FALSE, filterAerosol_climatology = FALSE, filterAerosol_low = FALSE, filterAerosol_moderate = FALSE, filterAerosol_high = FALSE)

#terra::plot(terra::rast(list.files("C:/Users/miles/OneDrive/Dokumente/EAGLE/karlakolumna/masked", full.names=T)[1])[[1:2]])

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
